Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Sionet => Simonet

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName, based on Pottier and Sionet's \origLang.  This
marks the first step towards writing a verified compiler for a language with
information flow types.  Although we did not complete the full noninterference
proof, we were able to find subtle inaccuracies in the \origLang proofs.  
We discuss what would be involved in completing the proof and how this 
relates to other work.

>>>>

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName, based on
Pottier and Simonet's \origLang.  This
marks the first step towards writing a verified compiler for a language with
information flow types.  Although we did not complete the full noninterference
proof, we were able to find subtle inaccuracies in the \origLang proofs.  
We discuss what would be involved in completing the proof and how this 
relates to other work.
